### 2025-03-28 sup/sup.tex

\caption{\label{fig-compare}Allometric relationships between tree height
and crown radius versus DBH for angiosperms (a, c) and gymnosperms (b,
d) based on three different models: power-law (orange), generalized
Michaelis-Menten (green), and Weibull (blue). The density of overlapping
points is represented using a colour gradient ranging from black (low
density) to yellow (high density). Point density was calculated using a
2D kernel density estimation on a 300 \(\times\) 300 grid, which
estimate the concentration of data points in the log-transformed DBH and
tree height or crown radius. All axes are shown on the log scale.}

>>>>

\caption{\label{fig-compare}Allometric relationships between DBH and
tree height or crown radius in angiosperms (a, c) and gymnosperms (b,
d), based on three different models: power-law (orange), generalized
Michaelis-Menten (green), and Weibull (blue). A color gradient from
black (low density) to yellow (high density) indicates the density of
overlapping data points, calculated via 2D kernel density estimation on
a 300\,\(\times\)\,300 grid. All axes are shown on the log scale.}
